---
title: "Find Mean"
author: Kashish Doshi
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# findMean

<!-- badges: start -->
<!-- badges: end -->

The goal of findMean is to find the mean of one column grouped by another column and add it to the original data-set.  

## Installation

You can install the released version of findMean from [Github](https://github.com) with:

```{r eval = FALSE}
devtools::install_github("stat545ubc-2021/functions-kashishdoshi/findMean", 
                         ref = "0.1.0")
```


## Examples

This is a basic example of find_mean which adds a column containing means of the lifeExp column in the gapminder dataset

```{r example}
suppressPackageStartupMessages(library(findMean))
suppressPackageStartupMessages(library(gapminder))


lifeExp_mean <- if (!requireNamespace("gapminder", quietly = TRUE)) {
  stop("Package \"gapminder\" is needed to run this example. Please install or load it before running", 
       .call = FALSE)
  } else {
  find_mean(gapminder, lifeExp)
  }
```


This is another example of find_mean that also uses the optional grouping parameter

```{r}
lfExp_mean_country <- if (!requireNamespace("gapminder", quietly = TRUE)) {
  stop("Package \"gapminder\" is needed to run this example. Please install or load it before running", 
       .call = FALSE)
  } else {
  find_mean(gapminder, lifeExp, country)
  }
```
